---
title: "Anova testing Accuracy"
output:
  pdf_document: default
  html_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Hypothesis Testing for 8 interaction technique's Accuracy:


```{r dataAnalysis}
#Inputting Data: Analysis Excel sheet has "Accuracy" data of 8 interaction techniques
library(openxlsx)
library(stats)
library(gridExtra)
library(grid)
data <- read.xlsx("Analysis.xlsx",colNames = FALSE, sheet="Accuracy")
#Transpose
Accuracy<- c(data[,1], data[,2], data[,3], data[,4], data[,5],
                 data[,6], data[,7], data[,8])
techniques <- c(rep('technique1', 8),rep('technique2', 8),rep('technique3', 8),
                rep('technique4', 8),rep('technique5', 8),rep('technique6', 8),
                rep('technique7', 8),rep('technique8', 8))
combine <- cbind(Accuracy, techniques)

```

## Computing Mean and Standard Deviation of 8 technique's accuracy
```{r meanResults}
mean1<- mean(data$X1)
sd1 = sqrt(var(data$X1))
mean2<- mean(data$X2)
sd2 = sqrt(var(data$X2))
mean3<- mean(data$X3)
sd3 = sqrt(var(data$X3))
mean4<- mean(data$X4)
sd4 = sqrt(var(data$X4))
mean5<- mean(data$X5)
sd5 = sqrt(var(data$X5))
mean6<- mean(data$X6)
sd6 = sqrt(var(data$X6))
mean7<- mean(data$X7)
sd7 = sqrt(var(data$X7))
mean8<- mean(data$X8)
sd8 = sqrt(var(data$X8))

# Print in table
r1 <- c("Technique id", "Mean", "Standard Deviation")
r2 <- c("1", round(mean1, 2), round(sd1, 2))
r3 <- c("2", round(mean2, 2), round(sd2, 2))
r4 <- c("3", round(mean3, 2), round(sd3, 2))
r5 <- c("4", round(mean4, 2), round(sd4, 2))
r6 <- c("5", round(mean5, 2), round(sd5, 2))
r7 <- c("6", round(mean6, 2), round(sd6, 2))
r8 <- c("7", round(mean7, 2), round(sd7, 2))
r9 <- c("8", round(mean8, 2), round(sd8, 2))
tab <- rbind(r1, r2, r3, r4, r5, r6, r7,r8,r9)
grid.table(tab, rows = NULL)

```

## Anova Tests : Mean Accuracy




Study Populations: We have 8 participants in total to test 8 interaction techniques

Research hypotheses: at least one population mean accuracy is different from the rest.


Null hypotheses:  all the population means accuracy  are equal

```{r AnovaResults}
results <- aov(Accuracy ~ techniques)
anova(results)
```

The decision is to reject the null hypothesis, as the p-value is < 0.05.
There is sufficient evidence to see that the mean values for all techniques are not
all equal. At least two of these techniques has mean values that were different from each
other.

## Creating side by side box plots

```{r plot}
boxplot(Accuracy~techniques,main = "Comparing Accuracy of 8 Techniques",   
        xlab = "Techniques Number", ylab = "Accuracy ( 0 to 1)")
```

The boxplots show that the differences in performance in terms of accuracy for techniques (1,6), (1, 7) and (1,8) 
due to how little of the boxplots “overlap”. However,
techniques 6,7,8 overlap significantly, so there will likely be some similarities.
Additionally, techniques 1,2,3,4 and 5 also overlap quite a bit, indicating
that we may find some similarities in those techniques as well. This is supported by
the mean of techniques 1 and 3 being similar to each other, as well as the
mean of the techniques 1 and 2 and 1 and 5 having similar means. It is also evident that the
techniques (8,3), (6,5), (7,5) and (8,5) have more of a difference in their means.



## Tukey HSD (Honest Significant Difference) post hoc comparision
A pairwise comparison technique that uses the Studentized range distribution to construct simultaneous confidence
intervals for differences of all pairs of means. Studentization means dividing a
mean value by its standard error. We are computing the Tukey HSD with confidence level of 0.95.

```{r tukey}
TukeyHSD(results, conf.level=0.95)
```

As we can see from the table above, techniques (6,1) has p(= 0.0039106) < 0.05, techniques (7,1) has p(= 0.0005165) < 0.05, techniques (8,1) has p(= 0.0002552) < 0.05. Also, it is evident that techniques(8,3) has  p(= 0.0306076) < 0.05, techniques (6,5) has  p(= 0.0282231) < 0.05, techniques (7,5) p(= 0.0046266) < 0.05 and techniques (8,5) p(= 0.0024188) < 0.05
SO we can conclude that technique 1 has different mean than technique 6,7 and 8.Also,  technique 5 has different mean than technique 6,7 and 8.  Therefore, technique 1 and 5 is significantly more accurate than technique 6,7,8.  


