---
title: "ANOVA Testing in R studios"
output: pdf_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hypothesis Testing for 8 interaction techniques:


```{r dataAnalysis}
#Inputing Data: Analysis Excel sheet has "Time" data of 8 interaction techniques
library(openxlsx)
library(stats)
library(gridExtra)
library(grid)
data <- read.xlsx("Analysis.xlsx",colNames = FALSE, sheet="Time")
#Transpose
time <- c(data[,1], data[,2], data[,3], data[,4], data[,5],
                 data[,6], data[,7], data[,8])
techniques <- c(rep('technique1', 8),rep('technique2', 8),rep('technique3', 8),
                rep('technique4', 8),rep('technique5', 8),rep('technique6', 8),
                rep('technique7', 8),rep('technique8', 8))
combine <- cbind((time), techniques)

```

## Computing Mean and Standard Deviation of 8 techniques
```{r meanResults}
mean1<- mean(data$X1)
sd1 = sqrt(var(data$X1))

mean2<- mean(data$X2)
sd2 = sqrt(var(data$X2))

mean3<- mean(data$X3)
sd3 = sqrt(var(data$X3))

mean4<- mean(data$X4)
sd4 = sqrt(var(data$X4))

mean5<- mean(data$X5)
sd5 = sqrt(var(data$X5))

mean6<- mean(data$X6)
sd6 = sqrt(var(data$X6))

mean7<- mean(data$X7)
sd7 = sqrt(var(data$X7))

mean8<- mean(data$X8)
sd8 = sqrt(var(data$X8))

# Print in table
r1 <- c("Technique id", "Mean", "Standard Deviation")
r2 <- c("1", round(mean1, 2), round(sd1, 2))
r3 <- c("2", round(mean2, 2), round(sd2, 2))
r4 <- c("3", round(mean3, 2), round(sd3, 2))
r5 <- c("4", round(mean4, 2), round(sd4, 2))
r6 <- c("5", round(mean5, 2), round(sd5, 2))
r7 <- c("6", round(mean6, 2), round(sd6, 2))
r8 <- c("7", round(mean7, 2), round(sd7, 2))
r9 <- c("8", round(mean8, 2), round(sd8, 2))
tab <- rbind(r1, r2, r3, r4, r5, r6, r7,r8,r9)
grid.table(tab, rows = NULL)

```

## Anova Tests : Mean Time Completion

An ANOVA test is a type of statistical test used to determine if there is a statistically significant difference between two or more categorical groups by testing for differences of means using variance.



Study Populations: We have 8 participants in total to test 8 interaction techniques

Research hypotheses: at least one population mean of completion time is different from the rest.


Null hypotheses:  all the population means of completion time are equal

```{r AnovaResults}
results <- aov(time ~ techniques)
anova(results)
```

The decision is to reject the null hypothesis, as the p-value is < 0.05.
There is sufficient evidence to see that the mean values for all techniques are not
all equal. At least two of these techniques has mean values that were different from each
other.

## Creating side by side box plots

```{r plot}
boxplot(time~techniques,main = "Comparing time Performance of 8 Techniques", 
        xlab = "Techniques Number", ylab = "Completion time (ms)")
```

The boxplots show that the differences in performance in terms of time for techniques 4,5 and 4, 7
due to how little of the boxplots “overlap”. However,
technique 1,2,3,4 and 8 overlap significantly, so there will likely be some similarities.
Additionally, techniques 5,6,7 also overlap quite a bit, indicating
that we may find some similarities in those techniques as well. This is supported by
the mean of techniques 5 and 7 being similar to each other, as well as the
mean of the techniques 1 and 8 having similar means. It is also evident that the
techniques 4, 5 and 4, 7 have more of a difference in their means.



## Tukey HSD (Honest Significant Difference) post hoc comparision
A pairwise comparison technique that uses the Studentized range distribution to construct simultaneous confidence
intervals for differences of all pairs of means. Studentization means dividing a
mean value by its standard error. We are computing the Tukey HSD with confidence level of 0.95.

```{r tukey}
TukeyHSD(results, conf.level=0.95)
```

As we can see from the table above, technique 5 technique 4 has p(= 0.0387199) < 0.05 and technique 7 and technique 4 has p(= 0.0272632) < 0.05. SO we can conclude that technique 4 has different mean than technique 5 and 7. Therefore, technique 4 is significantly faster than technique 5 and 7.  


